\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage[
    colorlinks=true,
    urlcolor=gray,
    linkcolor=gray,
    citecolor=gray
]{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\setlength{\parindent}{0pt}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\begin{document}

% Header
\begin{center}
    {\LARGE Jishnu Jayaprakash} \\
    Software Engineer \\
    % \faEnvelopeO~\href{mailto:first.last@resumeworded.com}{\textcolor{gray}{jishnujp.me}} \quad
    \faLinkedinSquare~\href{https://www.linkedin.com/in/jishnu-jayaprakash-813488156}{\textcolor{gray}{LinkedIn}} \quad
    \faTwitter~\href{https://x.com/Jishnu_J_P}{\textcolor{gray}{Jishnu\_J\_P}} \quad
    \faGithub~\href{https://github.com/jishnujp}{\textcolor{gray}{GitHub}} \quad
    \faGlobe~\href{https://jishnujp.me}{\textcolor{gray}{jishnujp.me}} \quad

\end{center}

\vspace{0.5em}

% EXPERIENCE
\section*{EXPERIENCE}

\textbf{Valuepitch E Technologies} \hfill \textit{Aug 2024 -- Present} \\
\textit{Software Development Consultant} \hfill \textit{Remote} \begin{itemize}[leftmargin=*]
    \item Architected and maintained high-availability cloud infrastructure for Frappe applications, implementing automated monitoring and disaster recovery systems.
    \item Designed scalable N8N workflow automation infrastructure and comprehensive cloud monitoring platforms for enterprise products.
    \item Managed multiple in-house applications within the Frappe ecosystem, ensuring seamless integration and optimal performance.
\end{itemize}


\textbf{NSE Academy \& RCSS} \hfill \textit{Feb 2025 -- Apr 2025} \\
\textit{Educator - Python for Finance} \hfill \textit{Kochi, India} \begin{itemize}[leftmargin=*]
    \item Led an intensive Python programming course covering stock market fundamentals, automated trading systems, and AI applications in financial analysis.
    \item Developed and delivered hands-on projects including real-time price alert systems and market analysis tools for BCom and BBA students.
\end{itemize}


\textbf{Valuepitch E Technologies} \hfill \textit{Nov 2022 -- Aug 2024} \\
\textit{Software Engineer} \hfill \textit{Remote} \begin{itemize}[leftmargin=*]
    \item Developed a scalable speech-to-text platform using OpenAI Whisper and AWS Transcribe, increasing transcription team productivity by 4 times.
    \item Engineered an AI-powered image segmentation service using Meta's SAM, reducing manual processing time while maintaining high accuracy.
    \item Built an automated legal document analysis system using LLM agents, reducing processing time while ensuring high accuracy in document analysis.
\end{itemize}

% PROJECTS
\section*{PROJECTS}

\textbf{QuantQuest – Paradox ’25, IITM} \\
Ideated, designed, and led the development of QuantQuest, a statistics-based strategic game at Paradox ’25, IITM BS Degree's annual tech fest. Built games where participants exploited statistical edges and placed API-based bets using virtual wallets; managed concept design, game logic, API infrastructure, deployment, and logistics. \\
\faGithub~\href{https://github.com/21f1006194/quant-quest}{\textcolor{gray}{repo}} \, \textbar{} \,
\faPlayCircle~\href{https://youtu.be/zgA83sge67Y?t=1211}{\textcolor{gray}{demo}} 

\textbf{Household Services} \\
A multi-user platform for booking and managing home services, enabling customers to find professionals, book appointments, and track requests. Admins oversee provider approvals and platform operations. Built with Flask and Python. \\
\faGithub~\href{https://github.com/21f1006194/Household-Services}{\textcolor{gray}{repo}} \, \textbar{} \,
\faPlayCircle~\href{https://www.youtube.com/watch?v=FHMdtaLWznI}{\textcolor{gray}{demo}} 

\pagebreak

\textbf{Business Analysis} \\
Analyzed business data for a local juice bar, providing actionable insights and recommendations using descriptive analytics. Includes a certificate of completion. \\
\faGithub~\href{https://github.com/jishnujp/avocado-analysis}{\textcolor{gray}{repo}} \, \textbar{} \,
\faPlayCircle~\href{https://www.youtube.com/watch?v=u5RuEhBsXKg}{\textcolor{gray}{demo}} \, \textbar{} \,
\faFilePdfO~\href{https://raw.githubusercontent.com/jishnujp/avocado-analysis/main/public/certificate.pdf}{\textcolor{gray}{certificate}} 

\textbf{US Senate Roll Call Analysis} \\
Performed data analysis on US Senate voting records, visualizing patterns and outcomes for legislative sessions using Python. \\
\faGithub~\href{https://github.com/jishnujp/US_senate_roll_call}{\textcolor{gray}{repo}} 

\textbf{Vaccine Search} \\
Developed a Python app to search and notify users of available COVID-19 vaccine slots in India, integrating with public APIs for real-time results. \\
\faGithub~\href{https://github.com/jishnujp/vaccine_search}{\textcolor{gray}{repo}} 

\textbf{Security Tools} \\
Created a tool to check password exposure using the k-anonymity model and haveibeenpwned API. Includes a web interface for public use. \\
\faGithub~\href{https://github.com/jishnujp/securityTools}{\textcolor{gray}{repo}} \, \textbar{} \,
\faGlobe~\href{https://jishnujp.github.io/securityTools}{\textcolor{gray}{try it}} 

% EDUCATION
\section*{EDUCATION}
\textbf{Indian Institute of Technology, Madras} \hfill \textit{Present} \\
Bachelor's in Programming and Data Science

\textbf{College of Engineering, Chengannur} \hfill \textit{2015 -- 2019} \\
Bachelor's Degree in Electronics \& Communication

% CERTIFICATIONS
\section*{CERTIFICATIONS}
\textbf{Diploma in Data Science}, IIT Madras \\
Intermediary Level (Diploma) in the Bachelor's degree program. Coursework: Mathematics, Statistics, Machine Learning, Business Analytics, Data Management. \\
\href{https://jishnujp.github.io/certificates/data_science_diploma.pdf}{\faFilePdfO~\textcolor{gray}{View Certificate}}

\textbf{Social Networks}, IIT Madras \\
Studied social network graphs and their properties using Python. \\
\href{https://archive.nptel.ac.in/content/noc/NOC22/SEM1/Ecertificates/106/noc22-cs30/Course/NPTEL22CS30S4373058402018648.jpg}{\faFilePdfO~\textcolor{gray}{View Certificate}}

\textbf{Data Science Toolbox}, Johns Hopkins \\
Overview of essential tools for data analysts. \\
\href{https://coursera.org/share/bd0023b71386ae9c7246bad3d5b566a7}{\faFilePdfO~\textcolor{gray}{View Certificate}}

\textbf{Data Science Maths Skills}, Duke University \\
Introduction to core math and statistics for data science. \\
\href{https://coursera.org/share/4bcf67532cd1ae69781e51db0bbb3445}{\faFilePdfO~\textcolor{gray}{View Certificate}}

% WORKSHOPS
\section*{WORKSHOPS}
\textbf{Machine Learning in Medical Imaging}, IIT Madras \\
Overview of ML applications in medical image diagnosis. \\
\href{https://jishnujp.github.io/certificates/mlmedic.jpg}{\faFilePdfO~\textcolor{gray}{View Certificate}}

\textbf{Ethical Hacking}, Sree Buddha \\
Hands-on guide to discovering system vulnerabilities. \\
\href{https://jishnujp.github.io/certificates/ethical_hacking.jpg}{\faFilePdfO~\textcolor{gray}{View Certificate}}

\textbf{FOSSMeet}, NIT Calicut \\
Workshops on GoLang and web automation with Selenium and Python. \\
\href{https://jishnujp.github.io/certificates/fossmeet.jpg}{\faFilePdfO~\textcolor{gray}{View Certificate}}

\textbf{PyCEC}, CEC \\
Hands-on sessions on image processing, web scraping, and ML with Python. \\
\href{https://jishnujp.github.io/certificates/pycec.jpg}{\faFilePdfO~\textcolor{gray}{View Certificate}}

\end{document}
